Flattering Advice: Avoiding Disappointment in Advice-Giving

### 2025-01-30 manuscript/manuscript.qmd
Correct typo

Just as advisers may hesitate to provide unwelcome truths, advisees themselves are o
ften resistant to hearing them. People go to great lengths to avoid unpleasant information,
People often go to great lengths to avoid unpleasant information,
deriving belief-based utility from maintaining favorable views of
themselves [@Golman2017; @Ho2018; @Loewenstein2018]. Moreover, they
often prefer advisers who withhold bad news from them [@Shalvi2019] and
punish those who communicate bad news [@John2019]. Advisers,
anticipating these preferences and consequences face a dilemma: Should
they provide the accurate but potentially painful truth, or shade their
recommendations to preserve the advisee's mood and the adviser's own
standing? Advisers who fear they will be blamed or disliked for
undermining someone's confidence may reasonably avoid candid feedback,
particularly if they don't incur a cost when the advisee makes a
mistake.

>>>>

Just as advisers may hesitate to provide unwelcome truths, advisees themselves are often 
resistant to hearing them. People often go to great lengths to avoid unpleasant information,
deriving belief-based utility from maintaining favorable views of
themselves [@Golman2017; @Ho2018; @Loewenstein2018]. Moreover, they
often prefer advisers who withhold bad news from them [@Shalvi2019] and
punish those who communicate bad news [@John2019]. Advisers,
anticipating these preferences and consequences face a dilemma: Should
they provide the accurate but potentially painful truth, or shade their
recommendations to preserve the advisee's mood and the adviser's own
standing? Advisers who fear they will be blamed or disliked for
undermining someone's confidence may reasonably avoid candid feedback,
particularly if they don't incur a cost when the advisee makes a
mistake.

### 2025-01-30 manuscript/manuscript.tex
Correct typo

Just as advisers may hesitate to provide unwelcome truths, advisees
themselves are o ften resistant to hearing them. People go to great
lengths to avoid unpleasant information, People often go to great
lengths to avoid unpleasant information, deriving belief-based utility
from maintaining favorable views of themselves (Golman et al., 2017; Ho
et al., 2021; Loewenstein \& Molnar, 2018). Moreover, they often prefer
advisers who withhold bad news from them (Shalvi et al., 2019) and
punish those who communicate bad news (John et al., 2019). Advisers,
anticipating these preferences and consequences face a dilemma: Should
they provide the accurate but potentially painful truth, or shade their
recommendations to preserve the advisee's mood and the adviser's own
standing? Advisers who fear they will be blamed or disliked for
undermining someone's confidence may reasonably avoid candid feedback,
particularly if they don't incur a cost when the advisee makes a
mistake.

>>>>

Just as advisers may hesitate to provide unwelcome truths, advisees
themselves are often resistant to hearing them. People often go to great
lengths to avoid unpleasant information, deriving belief-based utility
from maintaining favorable views of themselves (Golman et al., 2017; Ho
et al., 2021; Loewenstein \& Molnar, 2018). Moreover, they often prefer
advisers who withhold bad news from them (Shalvi et al., 2019) and
punish those who communicate bad news (John et al., 2019). Advisers,
anticipating these preferences and consequences face a dilemma: Should
they provide the accurate but potentially painful truth, or shade their
recommendations to preserve the advisee's mood and the adviser's own
standing? Advisers who fear they will be blamed or disliked for
undermining someone's confidence may reasonably avoid candid feedback,
particularly if they don't incur a cost when the advisee makes a
mistake.
